---
title: "R Amanda"
output: html_document
date: "2023-05-10"
---

```{r setup, include=FALSE}
library(readxl)
library(lubridate)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(lme4)
library(tidyr)
library(dplyr)
```


reading in data
```{r}
data <- read_excel("C:/Users/holze/Documents/Temporal stability/temp_riskperception/ruv/data/ruv_risks.xlsx", sheet = "data")
dates <- read_excel("C:/Users/holze/Documents/Temporal stability/temp_riskperception/ruv/data/ruv_risks.xlsx", sheet = "dates")

data_in <- read_excel("C:/Users/holze/Documents/Temporal stability/temp_riskperception/ruv/data/inflation.xlsx", sheet = "year")

data_a <- read_excel("C:/Users/holze/Documents/Temporal stability/temp_riskperception/ruv/data/unemployment.xlsx", sheet = "A")
```


```{r}
class(data_a$unemployment)
```


Wrangle data from inflation
```{r}
data_in <- subset(data_in, select = -c(2:4,6))

df_wide <- pivot_wider(data_in, names_from = wave, values_from = inflation)

# add new column using $
df_wide$risk_de <- "inflation"
```

wrangle data from unemployment
```{r}
data_a <- subset(data_a, select = -2)

df_widea <- pivot_wider(data_a, names_from = wave, values_from = unemployment)

# add new column using $
df_widea$risk_de <- "unemployment"

```

combine all the data
```{r}
# combine data frames using rbind()
data <- rbind(data, df_wide)
data <- rbind(data, df_widea)

```


Wrangle data 
```{r}
# pivot data to long format
data <- pivot_longer(data, cols= 2:32,values_to="value",names_to="wave")
 
# merge data with date information
data <- left_join(data, dates, by = "wave")

# delete NAs, create a numeric wave variable, rename risk_de to risk, and transform txt variables into factors
data <- data %>% 
  filter(!is.na(value)) %>% 
  mutate(wave_num=parse_number(wave)) %>% 
  rename(risk = risk_de) %>% 
  mutate(risk = factor(risk))
  
  #mutate(wave = factor(wave)) %>% 
  #mutate(food = factor(food))

# select risks that have been measured at least twice
selection <- data %>% 
  group_by(risk) %>% 
  summarize(n_waves=n()) %>% 
  ungroup()

data <- left_join(data,selection, by="risk") %>% 
  filter(n_waves > 2)

data$value <- ave(data$value, data$risk, FUN = function(x) scale(x))
```


Plot the data: First Plot 
```{r}


# plot time course of risk perception
ggplot(data = data, mapping = aes(x = year, y = value, cluster = risk)) + 
  geom_line(color="grey") +
  ylim(c(-3,3)) +
  xlab("Year") + 
  ylab("High Risk (% Sample)") + 
  theme_minimal() +
  theme(legend.position = "none")

  #scale_x_datetime(limits = as.POSIXct(strptime(c("2014-01-01 12:00","2025-12-01 12:00"), format = "%Y-%m-%d %H:%M"))) 
```


Show inflation line
```{r}

data_sel<- data %>% 
  filter(risk == "inflation")
  
data_label<- data %>% 
  filter(risk == "inflation") %>% 
  filter(year == max(year))

# plot time course of risk perception
ggplot(data = data, aes(x = year, y = value, cluster = risk)) + 
  geom_line(color="grey") +
  ylim(c(-3,3)) +
  xlab("Year") + 
  ylab("High Risk (% Sample)") + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_line(data=data_sel,mapping=aes(x = year, y = value),color="orange",linewidth=2) +
  geom_text(data=data_label,size=4.5,mapping=aes(label=risk,
                                        x = year, 
                                        y = value),color="orange",lwd=1.5,hjust=1, vjust = 0, nudge_y = 40) 

  #scale_x_datetime(limits = as.POSIXct(strptime(c("2014-01-01 12:00","2025-12-01 12:00"), format = "%Y-%m-%d %H:%M")))

```


show unemployment line 
```{r}

data_sol<- data %>% 
  filter(risk == "unemployment")
  
data_label<- data %>% 
  filter(risk == "unemployment") %>% 
  filter(year == max(year))

# plot time course of risk perception
ggplot(data = data, aes(x = year, y = value, cluster = risk)) + 
  geom_line(color="grey") +
  ylim(c(-3,3)) +
  xlab("Year") + 
  ylab("High Risk (% Sample)") + 
  theme_minimal() +
  theme(legend.position = "none") +
  geom_line(data=data_sol,mapping=aes(x = year, y = value),color="orange",linewidth=2) +
  geom_text(data=data_label,size=4.5,mapping=aes(label=risk,
                                        x = year, 
                                        y = value),color="orange",lwd=1.5,hjust=1, vjust = 0, nudge_y = 40) 

  #scale_x_datetime(limits = as.POSIXct(strptime(c("2014-01-01 12:00","2025-12-01 12:00"), format = "%Y-%m-%d %H:%M")))

```


Define data for correlation 
```{r}
df <- subset(data, risk == c("inflation", "steigende Lebenshaltungskosten"))

df_a <- subset(data, risk == "inflation")
df_c <- subset(data, risk == "steigende Lebenshaltungskosten")
df_d <- subset(data, risk == "unemployment")
```


Plot an correlation of inflation and steigende Lebenshaltungskosten
```{r}
B <- ggplot(data = NULL, aes(x = df_c$value, y = df_a$value)) +
  geom_point() +
  xlab("steigende Lebenshaltungskosten") +
  ylab("inflation") +
  ggtitle("correlation") +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal()

# Add a legend
B <- B + labs(color = "Risk")

# Display the plot
print(B)
```

Plot an correlation of unemployment and steigende Lebenshaltungskosten. Does not work yet because of diffrent lenght
```{r}
df_c2 <- df_c[-c(1:12), ]


C <- ggplot(data = NULL, aes(x = df_c2$value, y = df_d$value)) +
  geom_point() +
  xlab("steigende Lebenshaltungskosten") +
  ylab("unemployment") +
  ggtitle("correlation") +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal()

# Add a legend
C <- C + labs(color = "Risk")

# Display the plot
print(C)
```




```{r}
corr<- cor(df_a$value, df_c$value)
```

```{r}
ggplot(df, aes(x = year, y = value, color = risk)) +
  geom_point()
```

Correlation in group 
```{r}
p <- ggplot(df, aes(x = year, y = value, color = risk)) +
  geom_point()

# Korrelationslinie hinzufügen
p + geom_smooth(data = df_a, aes(x = year, y = value), method = "lm", se = FALSE, color = "red") +
    geom_smooth(data = df_c, aes(x = year, y = value), method = "lm", se = FALSE, color = "blue") +
  ggtitle(paste("Korrelation zwischen A und C: ", round(corr, 3)))
```


Correlation in Group
```{r}
ggplot(df, aes(x = year, y = value, color = risk)) +
  geom_point() +
  geom_smooth(data = df, aes(x = year, y = ifelse(risk == "inflation", value, NA)), method = "lm", se = FALSE, color = "red") +
  geom_smooth(data = df, aes(x = year, y = ifelse(risk == "steigende Lebenshaltungskosten", value, NA)), method = "lm", se = FALSE, color = "blue") +
  ggtitle(paste("Korrelation zwischen inflation und steigende Lebenshaltungskosten: ", round(corr, 3)))
```

```{r}
ggplot(df, aes(x = year, y = value, color = risk)) +
  geom_line()
```

```{r}
p <- ggplot(df, aes(x = year, y = value, color = risk)) +
  geom_point()

# Korrelationslinie hinzufügen
p + geom_smooth(data = df, aes(x = year, y = value), method = "lm", se = FALSE, color = "red") +
  ggtitle(paste("correlation between inlation and increasing living cost: ", round(corr, 3)))
```


Plot lagged correlation... code is from a website. It still needs adjusting. 
```{r}
# Calculate lagged variables
lag_years <- c(1, 2, 3)  # Specify the lagged years of interest

df_lagged <- df %>%
  mutate(
    inflation_lagged = lag(inflation, n = lag_years),
    perceived_risk_lagged = lag(perceived_risk, n = lag_years)
  ) %>%
  filter(!is.na(inflation_lagged) & !is.na(perceived_risk_lagged))

# Create a scatter plot with correlations
B <- ggplot(data = df_lagged, aes(x = perceived_risk_lagged, y = inflation_lagged)) +
  geom_point() +
  xlab("Perceived Risk (lagged)") +
  ylab("Actual Inflation (lagged)") +
  ggtitle("Correlation between Perceived Risk and Actual Inflation") +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  theme_minimal()

# Add a legend
B <- B + labs(color = "Risk")

# Display the plot
print(B)
```

