---
title: "Analysis"
author: "Amanda Holzer, Arzie Bajrami, Alexandra Bagaïni, Rui Mata"
date: "2024-06-25"
output: 
  html_document:
    number_sections: yes
    theme: cerulean
    df_print: paged
    code_folding: hide
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
# PACKAGES ---------------------------------------------------------------
#load packages 
#install.packages("dplyr")
#install.packages("here")
#install.packages("viridis")
#install.packages("tidyverse")
#install.packages("devtools")
library(dplyr)
library(here)
library(readr)
library(tidyverse)
library(ggplot2)
library(knitr)
library(viridis)
#library(flexplot)

# PATH ---------------------------------------------------------------
#set working directory
setwd(here())
here("temp_riskperception")
getwd()

# DATA ---------------------------------------------------------------
#Import the data set
df_final <- read_csv(here("data", "scoping_data.csv"))

```

# Scoping Review

This document visualizes the data for the scoping review.

## Study Designs Across Domains

This plot shows the number of studies using a longitudinal or serial cross-sectional design across several domains.s
```{r, warning=FALSE}
### plot domains with study design
### Function to create a single horizontal bar plot for counts of 1
create_combined_horizontal_bar <- function(df) {
  columns_of_interest <- c('health', 'finance', 'political', 'crime', 'nature', 'nuclear', 'social')
  
  # Create a long-format data frame for ggplot
 df_long <- df %>%
  tidyr::gather(key = "variable", value = "value", columns_of_interest) %>%
  filter(value == 1)
  
  # Arrange levels of 'variable' by count in ascending order
  df_long$variable <- factor(df_long$variable, levels = names(sort(table(df_long$variable), decreasing = FALSE)))
  
  # Define custom colors using hex color codes
  custom_colors <- c("#440154", "#22A884")  # Hex color codes without alpha
  
  # Plotting the horizontal bar plot using ggplot2
  ggplot(df_long, aes(x = value, y = variable, fill = study_design)) +
    geom_bar(stat = "identity", position = position_stack(reverse = TRUE), color = NA) +  # Reverse the stacking order
    scale_fill_manual(values = setNames(custom_colors, unique(df_long$study_design))) +  # Apply custom colors to study_design levels
    theme_minimal() +
    theme(panel.grid = element_blank(), panel.border = element_blank()) +  # Remove grid lines and borders
    labs(x = "Number of Studies", y = NULL, title = NULL) +  # Remove y-axis label and title
    xlab("Number of Studies")  # Set x-axis label
}
# Apply the function to df_final
create_combined_horizontal_bar(df_final)
```

## Measuring Risk Perception Across Domains

This plot shows the number of studies and how many times they measured risk perception across several domains.

```{r, warning=FALSE}
###plot domain with measurement points-----
#create measurement category with 2, 3, and 3+
df_final <- df_final %>%
  mutate(measure = ifelse(times_measured_1 == 2, "2",
                          ifelse(times_measured_1 == 3, "3", "3+")))

# Function to create a single horizontal bar plot for counts of 1
create_combined_horizontal_bar <- function(df) {
  columns_of_interest <- c('health', 'finance', 'political', 'crime', 'nature', 'nuclear', 'social')
  
  # Create a long-format data frame for ggplot
  df_long <- df %>%
    gather(key = "variable", value = "value", columns_of_interest) %>%
    filter(value == 1)  # Filter only rows where the value is 1
  
  # Arrange levels of 'variable' by count in ascending order
  df_long$variable <- factor(df_long$variable, levels = names(sort(table(df_long$variable), decreasing = FALSE)))
  
  # Plotting the horizontal bar plot using ggplot2 with Viridis color scale
  ggplot(df_long, aes(x = value, y = variable, fill = measure)) +
    geom_bar(stat = "identity", position = position_stack(reverse = TRUE), color = NA) +  # Reverse the stacking order
    scale_fill_viridis_d() +  # Use Viridis color palette for measure variable
    theme_minimal() +
    theme(panel.grid = element_blank(), panel.border = element_blank()) +  # Remove grid lines and borders
    labs(x = "Number of Studies", y = NULL, title = NULL) +  # Remove y-axis label and title
    xlab("Number of Studies")  # Set x-axis label
}

# Apply the function to df_final
create_combined_horizontal_bar(df_final)


```

## Risk Formulation Across Domains

This plot illustrates the different risk formulations used to measure risk perception across various domains.

```{r, warning=FALSE}
#kind of risk (risk, concern, worry)
create_combined_horizontal_bar <- function(df) {
  columns_of_interest <- c('health', 'finance', 'political', 'crime', 'nature', 'nuclear', 'social')
  
  # Create a long-format data frame for ggplot
  df_long <- df %>%
    gather(key = "variable", value = "value", columns_of_interest) %>%
    filter(value == 1)  # Filter only rows where the value is 1
  
  # Plotting the horizontal bar plot using ggplot2 with Viridis color scale
  ggplot(df_long, aes(x = variable, fill = as.factor(risk_1))) +
    geom_bar(position = "fill", stat = "count", color = "white") +
    coord_flip() +  # Flip the coordinates for a horizontal bar plot
    theme_minimal() +
    theme(panel.grid = element_blank(), panel.border = element_blank(),
          axis.text.x = element_blank(), axis.title.x = element_blank()) +  # Remove x-axis labels and title
    labs(x = NULL, y = NULL, title = NULL) +  # Remove axis labels and change title
    scale_fill_viridis_d(name = "Risk Formulation")  # Use Viridis color palette and customize legend title
}

# Apply the function to df_final
create_combined_horizontal_bar(df_final)
```

## Event Occurence Across Domains

This plot shows the occurrence of events across various domains.


```{r, warning=FALSE}

# Define the function
create_combined_horizontal_bar <- function(df) {
  columns_of_interest <- c('health', 'finance', 'political', 'crime', 'nature', 'nuclear', 'social')
  
  # Create a long-format data frame for ggplot
  df_long <- df %>%
    gather(key = "variable", value = "value", columns_of_interest) %>%
    filter(value == 1)  # Filter only rows where the value is 1
  
  # Create a new factor combining intervention and exposure columns into "event" and "no event"
  df_long$event_category <- ifelse(
    df_long$intervention_yesno_1 == 0 & df_long$exposure_yesno_1 == 0, 
    "No Event", 
    "Event"
  )
  
  # Plotting the horizontal bar plot using ggplot2 with Viridis color scale
  ggplot(df_long, aes(x = variable, fill = event_category)) +
    geom_bar(position = "fill", stat = "count", color = "white") +
    coord_flip() +  # Flip the coordinates for a horizontal bar plot
    theme_minimal() +
    theme(panel.grid = element_blank(), panel.border = element_blank(),
          axis.text.x = element_blank(), axis.title.x = element_blank()) +  # Remove x-axis labels and title
    labs(x = NULL, y = NULL, title = NULL) +  # Remove axis labels and change title
    scale_fill_viridis_d(name = "Event Occurence", labels = c("No Event", "Event"))  # Use Viridis color palette and customize legend title
}

# Apply the function to df_final
create_combined_horizontal_bar(df_final)

```


## Demographics Table Placeholder

Participant characteristics and demographics.

```{r, warning=FALSE}
#Table
```


# Temporal Stability


```{r, include=FALSE}
# Set CRAN mirror (choose a mirror appropriate for your location)
options(repos = c(CRAN = "https://cran.r-project.org"))

# PACKAGES ---------------------------------------------------------------
# install.packages("brms")
# install.packages("cmdstanr", repos = c("https://mc-stan.org/r-packages/", getOption("repos")), dependencies = TRUE)
# install.packages("loo")
# install.packages("bayesplot")
# install.packages("tidybayes")
# install.packages("posterior")
# install.packages("janitor")
# install.packages("openxlsx")
# install.packages("metafor")
# install.packages("tidyverse")
# install.packages("here")
# install.packages("readxl")
# install.packages("ggtext")

library(tidyverse)
library(brms)
library(cmdstanr)
library(loo)
library(bayesplot)
library(tidybayes)
library(posterior)
library(here)
library(janitor)
library(openxlsx)
library(metafor)
library(readxl)
library(ggtext)

# Function to install CmdStan (if needed)
#cmdstanr::install_cmdstan()

inv_logit <- function(x){plogis(x)}

# PATH ---------------------------------------------------------------
# set working directory
setwd(here())
getwd()

# DATA ---------------------------------------------------------------
# Prepare data file to get only relevant studies, i.e. studies with correlations
df_prep <- read_csv("data/scoping_data.csv")

# Cleaning columns names
df_prep <- clean_names(df_prep)

# Select relevant columns
selected_columns <- select(df_prep, x1,author, paper_title, study_design, risk_1:risk_5, 
                           intervention_yesno_1:intervention_yesno_5, temporal_analysis_1:temporal_analysis_5,
                           exposure_yesno_1:exposure_yesno_5, health, nature, crime, finance, 
                           nuclear, political, social, 
                           correlation_results_1_1:correlation_results_1_8, correlation_results_1:correlation_results_5, 
                           icc_results_1_1, test_retest_interval_1:test_retest_interval_5, 
                           type_participants_1:type_participants_5, sample_category_1:sample_category_5, 
                           age_category_1:age_category_5, country_1:country_5, sample_size_1:sample_size_5, 
                           prop_female_1:prop_female_5, mean_age_1:mean_age_5, sd_age_1:sd_age_5)

# Pivot the selected columns
df_pivoted <- selected_columns %>%
  mutate_all(as.character()) %>%
  mutate_if(is.logical, as.character) %>%
  mutate_if(is.double, as.character) %>%
  pivot_longer(-c(,x1, author, paper_title, study_design),  # Columns to exclude from pivot
               names_to = "var",
               values_to = "val")

# Filter out rows with NA values in the val column
df_filtered <- df_pivoted %>%
  filter(!is.na(val))

filtered_rows <- df_filtered %>%
  filter(var %in% paste0("temporal_analysis_", 1:5), val == 1)

# Group by ID (x1) variable and keep only those groups where all temporal_analysis values have val = 1
filtered_groups <- filtered_rows %>%
  group_by(x1) %>%
  filter(all(val == 1))

# Keep only x1 rows that satisfy the condition
df_filtered <- df_filtered %>%
  filter(x1 %in% filtered_groups$x1)

# Separate the var column into correlation_name and correlation_value
df_cor_results <- df_filtered %>%
  filter(str_detect(var, "correlation_results")) %>%
  separate(var, into = c("cor_name"), sep = ":")%>%
  rename(cor_val = val)

df_interval <- df_filtered %>%
  filter(str_detect(var, "test_retest_interval")) %>%
  separate(var, into = c("interval_name"), sep = ":") %>%
  rename(interval_val = val)%>%
  select(-author, -paper_title, -study_design)

# Add correlation interval
cor_num <- gsub("correlation_results_", "", df_cor_results$cor_name)

modified_interval_names <- paste0("test_retest_interval_", cor_num)

df_cor_results$interval_name <- modified_interval_names

df_cor <- merge(df_cor_results, df_interval, by = c("interval_name", "x1"), all.x = TRUE)

df_cor <- df_cor %>% select(-interval_name)

df_cor$cor_val <- as.numeric(df_cor$cor_val)

#### The rest of the data such as risk formulation, interval, sample size, age, female percentage, domain, subdomain, multi/single item, and Intervention/exposure were manually entered from the raw data in Excel.

## IMPORT CORRELATION FILE -----
library(readr)

df <- read_delim("data/masc_data.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)

spec(df)


## MEAN IMPUTATION FOR MISSING DATA -----
# Age
mean_age <- mean(df$age, na.rm=T)
mean_age
i_NA_age <- which(is.na(df$age) == TRUE)
df$age[i_NA_age] <- mean_age
mean_age == mean(df$age)

# Female percentage
mean_female <- mean(df$female, na.rm=T)
mean_female
i_NA_female <- which(is.na(df$female) == TRUE)
df$female[i_NA_female] <- mean_female
mean_female == mean(df$female)

## MANIPULATE DATA --------
mean(df$female, na.rm=T)
mean(df$age, na.rm=T)
df$interval_val <- df$interval_val/365
plot(df$interval_val, df$cor_val)


# Centering age and female percentage
df <- df %>% mutate(cor_val = if_else(cor_val <0,0, cor_val), 
                    age_dec_c = (age-40)/10,
                    age_dec_c2 = age_dec_c^2,
                    female_c = (female-0.50))

df <- escalc(measure = "COR", ri=cor_val, ni=n, data=df)
df$sei <- sqrt(df$vi)

# Creating domain groups
# health and other (social, political, crime, nature, finance)
df <- df %>% mutate(domain = 
                      case_when(domain %in% c("health") ~ "health",
                                !domain %in% c("health") ~ "other"))

# Creating event groups
# none and event (intervention or exposure)
df <- df %>% mutate(event = 
                      case_when(event %in% c("none") ~ "none",
                                !event %in% c("none") ~ "event"))

# Using sum contrast coding
sum_coding <- function(x, lvls = levels(x)) {
  # codes the first category with -1
  nlvls <- length(lvls)
  stopifnot(nlvls > 1)
  cont <- diag(nlvls)[, -nlvls, drop = FALSE]
  cont[nlvls, ] <- -1
  cont <- cont[c(nlvls, 1:(nlvls - 1)), , drop = FALSE]
  colnames(cont) <- lvls[-1]
  x <- factor(x, levels = lvls)
  contrasts(x) <- cont
  x
}

df <- df %>% 
  mutate(domain = factor(domain),
         domain = relevel(domain, ref="health"),
         domain = sum_coding(domain, lvls = levels(domain))) %>% 
  mutate(event = factor(event),
         event = relevel(event, ref="none"),
         event = sum_coding(event, lvls = levels(event))) %>% 
  mutate(item= factor(item),
         item = relevel(item, ref="multiple"),
         item = sum_coding(item, lvls = levels(item))) %>%
  mutate(formulation= factor(formulation),
         formulation = relevel(formulation, ref="risk"),
         formulation = sum_coding(formulation, lvls = levels(formulation)))

# Tables and plots
table(df$health_subdomain)
table(df$event)
table(df$item_c)

df %>% ggplot(aes(x = age)) + geom_histogram()
df %>% ggplot(aes(x = female)) + geom_histogram()
df %>% ggplot(aes(x = interval_val, y = cor_val)) + geom_point()


df %>% ggplot(aes(x = interval_val, y = cor_val)) + geom_point() + facet_grid(.~ event)
df %>% ggplot(aes(x = interval_val, y = cor_val)) + geom_point() + facet_wrap(.~ domain)
df %>% ggplot(aes(x = interval_val, y = cor_val)) + geom_point() + facet_wrap(.~ item)
```

## Model Fitting and Evaluation - Meta-Analytical Stability and Change Model (MASC)
### Model 1: Fitting with Correlation, Interval, and Size
```{r, code_folding = 'hide', warning=FALSE}
# Define family
family <- brmsfamily(
  family = "student",
  link = "identity"
)

# Define the formula
formula_m1 <- bf(
  cor_val | resp_se(sei, sigma = TRUE) ~ rel * (change * ((stabch^interval_val) - 1) + 1),
  nlf(rel ~ inv_logit(logitrel)),
  nlf(change ~ inv_logit(logitchange)),
  nlf(stabch ~ inv_logit(logitstabch)),
  logitrel ~ 1,
  logitchange ~ 1,
  logitstabch ~ 1,
  nl = TRUE
)

# Define the weakly informative priors
priors <- 
  prior(normal(0,1), nlpar="logitrel", class = "b") +
  prior(normal(0,1), nlpar="logitchange", class = "b") +
  prior(normal(0,1), nlpar="logitstabch", class = "b") +
  prior(cauchy(0,1), class = "sigma")

# Fit the model
fit_masc_m1 <- brm(
  formula = formula_m1,
  prior = priors,
  family = family,
  data = df,
  cores = 2,
  chains = 2,
  iter = 6000,
  warmup = 2000,
  control = list(max_treedepth = 10, adapt_delta = 0.95),
  seed = 1299
)

# Model summary
summary(fit_masc_m1)

# Plot conditional effects
plot(conditional_effects(fit_masc_m1), points = TRUE)

# Trace plots and parameter estimates
plot(fit_masc_m1, N = 5, ask = TRUE)

# Posterior predictive checks
pp_check(fit_masc_m1, type = "dens_overlay", ndraws = 100)
pp_check(fit_masc_m1, type = "stat", stat = "mean", ndraws = 1000, binwidth = .001)

# LOO and diagnostics
model_loo_m1 <- loo(fit_masc_m1, save_psis = TRUE, cores = 2)
plot(model_loo_m1, diagnostic = "k")
plot(model_loo_m1, diagnostic = "n_eff")

```


### Model 2a: Fitting with Demographics - Age, Age^2, Gender
```{r, warning=FALSE}
# Define family
family <- brmsfamily(
  family = "student",
  link = "identity"
)

# Define the formula
formula_m2a <- bf(
  cor_val | resp_se(sei, sigma = TRUE) ~ rel * (change * ((stabch^interval_val) - 1) + 1),
  nlf(rel ~ inv_logit(logitrel)),
  nlf(change ~ inv_logit(logitchange)),
  nlf(stabch ~ inv_logit(logitstabch)),
  logitrel ~ 1 + age_dec_c + age_dec_c2  + female_c,
  logitchange ~ 1 + age_dec_c + age_dec_c2 + female_c,
  logitstabch ~ 1 + age_dec_c + age_dec_c2 + female_c,
  nl = TRUE
)

# Define the weakly informative priors
priors <- 
  prior(normal(0,1), nlpar="logitrel", class = "b") +
  prior(normal(0,1), nlpar="logitchange", class = "b") +
  prior(normal(0,1), nlpar="logitstabch", class = "b") +
  prior(cauchy(0,1), class = "sigma")

# Fit the model
fit_masc_m2a <- brm(
  formula = formula_m2a,
  prior = priors,
  family = family,
  data = df,
  cores = 2,
  chains = 2,
  iter = 6000,
  warmup = 2000,
  control = list(max_treedepth = 10, adapt_delta = 0.95),
  seed = 1299
)

# Model summary
summary(fit_masc_m2a)

# Plot conditional effects
plot(conditional_effects(fit_masc_m2a), points = TRUE)

# Trace plots and parameter estimates
plot(fit_masc_m2a, N = 5, ask = TRUE)

# Posterior predictive checks
pp_check(fit_masc_m2a, type = "dens_overlay", ndraws = 100)
pp_check(fit_masc_m2a, type = "stat", stat = "mean", ndraws = 1000, binwidth = .001)

# Leave-One-Out (LOO) and diagnostics
model_loo_m2a <- loo(fit_masc_m2a, save_psis = TRUE, cores = 2)
plot(model_loo_m2a, diagnostic = "k")
plot(model_loo_m2a, diagnostic = "n_eff")

```


### Model 2b: Fitting with Measurement Characteristics - Domain, Item, Event
```{r, warning=FALSE}
# Define family
family <- brmsfamily(
  family = "student",
  link = "identity"
)

# Define the formula
formula_m2b <- bf(
  cor_val | resp_se(sei, sigma = TRUE) ~ rel * (change * ((stabch^interval_val) - 1) + 1),
  nlf(rel ~ inv_logit(logitrel)),
  nlf(change ~ inv_logit(logitchange)),
  nlf(stabch ~ inv_logit(logitstabch)),
  logitrel ~ 1 + domain + item + event,
  logitchange ~ 1 + domain + event,
  logitstabch ~ 1 + domain + event,
  nl = TRUE
)

# Define the weakly informative priors
priors <- 
  prior(normal(0,1), nlpar="logitrel", class = "b") +
  prior(normal(0,1), nlpar="logitchange", class = "b") +
  prior(normal(0,1), nlpar="logitstabch", class = "b") +
  prior(cauchy(0,1), class = "sigma")

# Fit the model
fit_masc_m2b <- brm(
  formula = formula_m2b,
  prior = priors,
  family = family,
  data = df,
  cores = 2,
  chains = 2,
  iter = 6000,
  warmup = 2000,
  control = list(max_treedepth = 10, adapt_delta = 0.95),
  seed = 1299
)

# Model summary
summary(fit_masc_m2b)

# Plot conditional effects
plot(conditional_effects(fit_masc_m2b), points = TRUE)

# Trace plots and parameter estimates
plot(fit_masc_m2b, N = 5, ask = TRUE)

# Posterior predictive checks
pp_check(fit_masc_m2b, type = "dens_overlay", ndraws = 100)
pp_check(fit_masc_m2b, type = "stat", stat = "mean", ndraws = 1000, binwidth = .001)

# Leave-One-Out (LOO) and diagnostics
model_loo_m2b <- loo(fit_masc_m2b, save_psis = TRUE, cores = 2)
plot(model_loo_m2b, diagnostic = "k")
plot(model_loo_m2b, diagnostic = "n_eff")

```


### Model 3: Fitting with Demographics and Measurement Characteristics - Domain, Item, Event, Formulation
```{r, warning=FALSE}
# Define the family
family <- brmsfamily(
  family = "student",
  link = "identity"
)

# Define the formula
formula_m3 <- bf(
  cor_val | resp_se(sei, sigma = TRUE) ~ rel * (change * ((stabch^interval_val) - 1) + 1),
  nlf(rel ~ inv_logit(logitrel)),
  nlf(change ~ inv_logit(logitchange)),
  nlf(stabch ~ inv_logit(logitstabch)),
  logitrel ~ 1 + age_dec_c + age_dec_c2 + female_c + domain + item + event + formulation,
  logitchange ~ 1 + age_dec_c + age_dec_c2 + female_c + domain + item + event + formulation,
  logitstabch ~ 1 + age_dec_c + age_dec_c2 + female_c + domain + item + event + formulation,
  nl = TRUE
)

# Define the weakly informative priors
priors <- 
  prior(normal(0, 1), nlpar = "logitrel", class = "b") +
  prior(normal(0, 1), nlpar = "logitchange", class = "b") +
  prior(normal(0, 1), nlpar = "logitstabch", class = "b") +
  prior(cauchy(0, 1), class = "sigma")

# Fit the model
fit_masc_m3 <- brm(
  formula = formula_m3,
  prior = priors,
  family = family,
  data = df,
  cores = 2,
  chains = 2,
  iter = 6000,
  warmup = 2000,
  control = list(max_treedepth = 10, adapt_delta = 0.95),
  seed = 1299
)

# MODEL 3 EVAL: MCMC DIAGNOSTICS --------------------------------------------------------

# Model summary
summary(fit_masc_m3)

# Plot conditional effects
plot(conditional_effects(fit_masc_m3), points = T)

# Trace plots & parameter estimates
plot(fit_masc_m3, N = 5, ask = TRUE)

# MODEL 3 EVAL: PP CHECKS --------------------------------------------------------
pp_check(fit_masc_m3, type = "dens_overlay", ndraws = 100)

pp_check(fit_masc_m3, type = "stat", stat = "mean", ndraws = 1000, binwidth = .001)

pp_check(fit_masc_m3, type = "stat", stat = "sd", ndraws = 500, binwidth = .001)

pp_check(fit_masc_m3, type = "stat", stat = "median", ndraws = 500, binwidth = .001)

pp_check(fit_masc_m3, type = "stat", stat = "mad", ndraws = 500, binwidth = .001)

pp_check(fit_masc_m3, type = "stat_2d")

pp_check(fit_masc_m3, type = "scatter_avg")

# MODEL 3 EVAL: LOO --------------------------------------------------------

# LOO & Pareto K
model_loo_m3 <- loo(fit_masc_m3, save_psis = TRUE, cores = 2)
plot(model_loo_m3, diagnostic = "k")
plot(model_loo_m3, diagnostic = "n_eff")

# LOO PIT
w <- weights(model_loo_m3$psis_object)
ppc_loo_pit_overlay(
  y = fit_masc_m3$data$cor_val,
  yrep = posterior_predict(fit_masc_m3),
  lw = w
)
ppc_loo_pit_qq(
  y = fit_masc_m3$data$cor_val,
  yrep = posterior_predict(fit_masc_m3),
  lw = w
)

# MODEL EVAL: LOO - COMPARISON OF ALL MODELS ----------------------------------------------------
loo1 <- loo(fit_masc_m1)
loo2a <- loo(fit_masc_m2a)
loo2b <- loo(fit_masc_m2b)
loo3 <- loo(fit_masc_m3)

loo_compare(loo1, loo2a, loo2b, loo3)

```


## Predictions Time

### Plot correlation and interval
```{r, warning=FALSE}

nd <- crossing(domain= NA,  
               sei = 0.1,
               item= NA, 
               event=NA,
               formulation=NA,
               age_dec_c= 0,
               age_dec_c2= 0,
               female_c= 0, 
               interval_val=seq(0,5, by = .1))

epred_draws_df <- nd %>% 
  add_epred_draws(fit_masc_m3, re_formula = NA)

ggplot(epred_draws_df) +
  stat_lineribbon(alpha = 1/4, point_interval = "mean_hdci", aes(x = interval_val, y = .epred)) + 
  geom_point(data= df, aes(x=interval_val, y= cor_val), size = 1.5, color = "grey20", alpha = 0.7) +
  theme_minimal() +
  labs(y = "Retest Correlation", x = "Retest Interval (Years)", color = "", linetype = "", fill = "",
       title = "Behaviour") +
  theme(strip.placement = "outside",
        legend.position = "none",
        legend.margin = margin(-.5,0,0,0, unit="cm"),
        legend.spacing.y = unit(0.15, 'cm'),
        legend.key.width = unit(1, "cm"),
        legend.key.size = unit(.3, "cm"),
        legend.text = element_text(size = 9, color = "grey20"),
        text = element_text(size = 9, color = "grey40"),
        axis.text.y = element_text(vjust=seq(0,1, length.out = 5)),
        axis.text.x = element_text(hjust=c(0,1)),
        title = element_text(size = 9, color = "grey20"),
        plot.tag  = element_text(size = 11, face = "bold", color = "grey20"),
        panel.spacing = unit(.5, "lines"),
        plot.title = element_blank(),
        panel.grid = element_blank(),
        plot.title.position = "plot",
        plot.margin = margin(b = 5, r = 5, l = 5),
        panel.background = element_rect(color = "grey75", fill = NA, size = .4)) +
  scale_fill_manual(values = c("#502a7b","#502a7c","#502a7a")) +
  guides(color = guide_legend(override.aes = list(size = .75)),
         fill = guide_legend(override.aes = list(size = .75)),
         size = "none", linetype = guide_legend(override.aes = list(size = .75))) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0,5)) +
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5))

```


### Plot correlation and interval by event
```{r, warning=FALSE}

nd <- crossing(domain= NA,  
               sei = 0.1,
               item= NA, 
               event= unique(df$event),
               formulation= NA,
               age_dec_c= 0,
               age_dec_c2= 0,
               female_c= 0, 
               interval_val=seq(0,5, by = .1))


epred_draws_df <- nd %>% 
  add_epred_draws(fit_masc_m3, re_formula = NA)

# epred_draws_dom <- epred_draws_df %>%
#   group_by(interval_val, health_subdomain) %>%
#   mean_hdci(.epred,.width = c(.95,.8,.5)) %>%
#   pivot_wider(names_from = .width, values_from = c(.lower,.upper))


# Set order and capitalise first letter
epred_draws_df$event <- str_to_title(epred_draws_df$event)

epred_draws_df$event<- factor(epred_draws_df$event, levels = c("None","Event"))

df_plot <- df %>% 
  mutate(event = str_to_title(event)) 

df_plot$event<- factor(df_plot$event, levels = c("None","Event"))

# Plot
p_event <- ggplot(epred_draws_df) +
  stat_lineribbon(alpha = 1/4, point_interval = "mean_hdci", aes(x = interval_val, y = .epred)) + 
  geom_point(data= df_plot, aes(x=interval_val, y= cor_val), size = 1.5, color = "grey20", alpha = 0.7) +
  # geom_line(data = epred_draws_agg,
  #           aes(x = time_diff_dec*10, y = .epred),
  #           color = "grey95",
  #           size = .5) +
  # geom_line(data = epred_draws_dom, 
  #           aes(x = time_diff_dec*10, y = .epred, linetype = domain_name),
  #           color = "#e07f00",
  #           linewidth = .25) +
  # geom_text_repel(data = lbl_dot_df, 
  #                 aes(x = time_diff_dec*10, y = .epred, label = label),
  #                 family = "Source Sans 3", size = 2.5,
  #                 min.segment.length = 0,
  #                 segment.color = "grey50",
  #                 segment.size = .25,
  #                 box.padding = 0.5,
  #                 nudge_x = .5,
  #                 nudge_y = c(.1, -.05)
  # ) +
  facet_wrap(.~event) +
  theme_minimal() +
  labs(y = "Retest Correlation", x = "Retest Interval (Years)", color = "", linetype = "", fill = "",
       title = "Behaviour") +
  theme(strip.placement = "outside",
        legend.position = "none", # c(0,0) bottom left, c(1,1) top-right.
        legend.margin = margin(-.5,0,0,0, unit="cm"),
        legend.spacing.y = unit(0.15, 'cm'),
        legend.key.width = unit(1, "cm"),
        legend.key.size = unit(.3, "cm"),
        # plot.tag.position = c(0,.8),
        legend.text = element_text(size = 10, color = "grey20"),
        text = element_text(size = 12, color = "grey40"),
        axis.text.y = element_text( vjust=seq(0,1, length.out = 5)),
        axis.text.x = element_text( hjust=c(0,1)),
        title = element_text(size = 12, color = "grey20"),
        plot.tag  = element_text( size = 12, face = "bold", color = "grey20"),
        panel.spacing = unit(.5, "lines"),
        plot.title = element_blank(),
        panel.grid = element_blank(),
        plot.title.position = "plot",
        plot.margin = margin(b = 5, r = 5, l = 5),
        panel.background = element_rect(color = "grey75", fill = NA, size = .4),
        strip.text = element_text(face = "bold"),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 12)) +
  scale_fill_manual(values = c("#502a7b","#502a7c","#502a7a" ))+
  guides(color = guide_legend(override.aes = list(size = .75)),
         fill =  guide_legend(override.aes = list(size = .75)),
         size = "none", linetype = guide_legend(override.aes = list(size = .75))) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0,5))+
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5))


p_event

ggsave(plot = p_event,
       filename = here::here("analysis", "masc_pred_event.jpeg"), 
       dpi = 300, width = 28, height = 30, units = "cm")

```


### Plot correlation and interval by domain
```{r, warning=FALSE}

nd <- crossing(domain= unique(df$domain),  
               sei = 0.1,
               item= NA, 
               event= NA,
               formulation= NA,
               age_dec_c= 0,
               age_dec_c2= 0,
               female_c= 0, 
               interval_val=seq(0,5, by = .1))


epred_draws_df <- nd %>% 
  add_epred_draws(fit_masc_m3, re_formula = NA)

# epred_draws_dom <- epred_draws_df %>%
#   group_by(interval_val, health_subdomain) %>%
#   mean_hdci(.epred,.width = c(.95,.8,.5)) %>%
#   pivot_wider(names_from = .width, values_from = c(.lower,.upper))


ggplot(epred_draws_df) +
  stat_lineribbon(alpha = 1/4, point_interval = "mean_hdci", aes(x = interval_val, y = .epred)) + 
  geom_point(data= df, aes(x=interval_val, y= cor_val), size = 1.5, color = "grey20", alpha = 0.7) +
  # geom_line(data = epred_draws_agg,
  #           aes(x = time_diff_dec*10, y = .epred),
  #           color = "grey95",
  #           size = .5) +
  # geom_line(data = epred_draws_dom, 
  #           aes(x = time_diff_dec*10, y = .epred, linetype = domain_name),
  #           color = "#e07f00",
  #           linewidth = .25) +
  # geom_text_repel(data = lbl_dot_df, 
  #                 aes(x = time_diff_dec*10, y = .epred, label = label),
  #                 family = "Source Sans 3", size = 2.5,
  #                 min.segment.length = 0,
  #                 segment.color = "grey50",
  #                 segment.size = .25,
  #                 box.padding = 0.5,
  #                 nudge_x = .5,
  #                 nudge_y = c(.1, -.05)
  # ) +
  facet_wrap(.~str_to_title(domain)) +
  theme_minimal() +
  labs(y = "Retest Correlation", x = "Retest Interval (Years)", color = "", linetype = "", fill = "",
       title = "Behaviour") +
  theme(strip.placement = "outside",
        legend.position = "none", # c(0,0) bottom left, c(1,1) top-right.
        legend.margin = margin(-.5,0,0,0, unit="cm"),
        legend.spacing.y = unit(0.15, 'cm'),
        legend.key.width = unit(1, "cm"),
        legend.key.size = unit(.3, "cm"),
        # plot.tag.position = c(0,.8),
        legend.text = element_text(size = 10, color = "grey20"),
        text = element_text(size = 12, color = "grey40"),
        axis.text.y = element_text( vjust=seq(0,1, length.out = 5)),
        axis.text.x = element_text( hjust=c(0,1)),
        title = element_text(size = 12, color = "grey20"),
        plot.tag  = element_text( size = 12, face = "bold", color = "grey20"),
        panel.spacing = unit(.5, "lines"),
        plot.title = element_blank(),
        panel.grid = element_blank(),
        plot.title.position = "plot",
        plot.margin = margin(b = 5, r = 5, l = 5),
        panel.background = element_rect(color = "grey75", fill = NA, size = .4),
        strip.text = element_text(face = "bold"),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 12)) +
  scale_fill_manual(values = c("#502a7b","#502a7c" , "#502a7a" )) +
  guides(color = guide_legend(override.aes = list(size = .75)),
         fill =  guide_legend(override.aes = list(size = .75)),
         size = "none", linetype = guide_legend(override.aes = list(size = .75))) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0,5))+
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5))


```



### Plot correlation and interval by item
```{r, warning=FALSE}

nd <- crossing(domain= NA,  
               sei = 0.1,
               item= unique(df$item), 
               event= NA,
               formulation= NA,
               age_dec_c= 0,
               age_dec_c2= 0,
               female_c= 0, 
               interval_val=seq(0,5, by = .1))


epred_draws_df <- nd %>% 
  add_epred_draws(fit_masc_m3, re_formula = NA)

# epred_draws_dom <- epred_draws_df %>%
#   group_by(interval_val, health_subdomain) %>%
#   mean_hdci(.epred,.width = c(.95,.8,.5)) %>%
#   pivot_wider(names_from = .width, values_from = c(.lower,.upper))

epred_draws_df  <- epred_draws_df  %>%
  mutate(item = str_to_title(as.character(item)))


ggplot(epred_draws_df) +
  stat_lineribbon(alpha = 1/4, point_interval = "mean_hdci", aes(x = interval_val, y = .epred)) + 
  geom_point(data= df, aes(x=interval_val, y= cor_val), size = 1.5, color = "grey20", alpha = 0.7) +
  # geom_line(data = epred_draws_agg,
  #           aes(x = time_diff_dec*10, y = .epred),
  #           color = "grey95",
  #           size = .5) +
  # geom_line(data = epred_draws_dom, 
  #           aes(x = time_diff_dec*10, y = .epred, linetype = domain_name),
  #           color = "#e07f00",
  #           linewidth = .25) +
  # geom_text_repel(data = lbl_dot_df, 
  #                 aes(x = time_diff_dec*10, y = .epred, label = label),
  #                 family = "Source Sans 3", size = 2.5,
  #                 min.segment.length = 0,
  #                 segment.color = "grey50",
  #                 segment.size = .25,
  #                 box.padding = 0.5,
  #                 nudge_x = .5,
  #                 nudge_y = c(.1, -.05)
  # ) +
  facet_wrap(.~str_to_title(item)) +
  theme_minimal() +
  labs(y = "Retest Correlation", x = "Retest Interval (Years)", color = "", linetype = "", fill = "",
       title = "Behaviour") +
  theme(strip.placement = "outside",
        legend.position = "none", # c(0,0) bottom left, c(1,1) top-right.
        legend.margin = margin(-.5,0,0,0, unit="cm"),
        legend.spacing.y = unit(0.15, 'cm'),
        legend.key.width = unit(1, "cm"),
        legend.key.size = unit(.3, "cm"),
        # plot.tag.position = c(0,.8),
        legend.text = element_text(size = 10, color = "grey20"),
        text = element_text(size = 12, color = "grey40"),
        axis.text.y = element_text( vjust=seq(0,1, length.out = 5)),
        axis.text.x = element_text( hjust=c(0,1)),
        title = element_text(size = 12, color = "grey20"),
        plot.tag  = element_text( size = 12, face = "bold", color = "grey20"),
        panel.spacing = unit(.5, "lines"),
        plot.title = element_blank(),
        panel.grid = element_blank(),
        plot.title.position = "plot",
        plot.margin = margin(b = 5, r = 5, l = 5),
        panel.background = element_rect(color = "grey75", fill = NA, size = .4) ,
        strip.text = element_text(face = "bold"),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 12))+ 
  scale_fill_manual(values = c("#502a7b","#502a7c" , "#502a7a" )) +
  guides(color = guide_legend(override.aes = list(size = .75)),
         fill =  guide_legend(override.aes = list(size = .75)),
         size = "none", linetype = guide_legend(override.aes = list(size = .75))) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0,5)) +
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5))

```



### Plot correlation and interval by formulation
```{r, warning=FALSE}

nd <- crossing(domain= NA,  
               sei = 0.1,
               item= NA, 
               event= NA,
               formulation= unique(df$formulation),
               age_dec_c= 0,
               age_dec_c2= 0,
               female_c= 0, 
               interval_val=seq(0,5, by = .1))


epred_draws_df <- nd %>% 
  add_epred_draws(fit_masc_m3, re_formula = NA)

# epred_draws_dom <- epred_draws_df %>%
#   group_by(interval_val, health_subdomain) %>%
#   mean_hdci(.epred,.width = c(.95,.8,.5)) %>%
#   pivot_wider(names_from = .width, values_from = c(.lower,.upper))


# Set order and capitalise first letter
epred_draws_df$formulation <- str_to_title(epred_draws_df$formulation)

epred_draws_df$formulation<- factor(epred_draws_df$formulation, levels = c("Risk","Concern", "Worry" ,"Threat"))

df_plot <- df %>% 
  mutate(formulation = str_to_title(formulation)) 

df_plot$formulation<- factor(df_plot$formulation, levels = c("Risk","Concern", "Worry" ,"Threat"))

# Plot
ggplot(epred_draws_df) +
  stat_lineribbon(alpha = 1/4, point_interval = "mean_hdci", aes(x = interval_val, y = .epred)) + 
  geom_point(data= df_plot, aes(x=interval_val, y= cor_val), size = 1.5, color = "grey20", alpha = 0.7) +
  # geom_line(data = epred_draws_agg,
  #           aes(x = time_diff_dec*10, y = .epred),
  #           color = "grey95",
  #           size = .5) +
  # geom_line(data = epred_draws_dom, 
  #           aes(x = time_diff_dec*10, y = .epred, linetype = domain_name),
  #           color = "#e07f00",
  #           linewidth = .25) +
  # geom_text_repel(data = lbl_dot_df, 
  #                 aes(x = time_diff_dec*10, y = .epred, label = label),
  #                 family = "Source Sans 3", size = 2.5,
  #                 min.segment.length = 0,
  #                 segment.color = "grey50",
  #                 segment.size = .25,
  #                 box.padding = 0.5,
  #                 nudge_x = .5,
  #                 nudge_y = c(.1, -.05)
  # ) +
  facet_wrap(.~formulation) +
  theme_minimal() +
  labs(y = "Retest Correlation", x = "Retest Interval (Years)", color = "", linetype = "", fill = "",
       title = "Behaviour") +
  theme(strip.placement = "outside",
        legend.position = "none", # c(0,0) bottom left, c(1,1) top-right.
        legend.margin = margin(-.5,0,0,0, unit="cm"),
        legend.spacing.y = unit(0.15, 'cm'),
        legend.key.width = unit(1, "cm"),
        legend.key.size = unit(.3, "cm"),
        # plot.tag.position = c(0,.8),
        legend.text = element_text(size = 10, color = "grey20"),
        text = element_text(size = 12, color = "grey40"),
        axis.text.y = element_text( vjust=seq(0,1, length.out = 5)),
        axis.text.x = element_text( hjust=c(0,1)),
        title = element_text(size = 12, color = "grey20"),
        plot.tag  = element_text( size = 12, face = "bold", color = "grey20"),
        panel.spacing = unit(.5, "lines"),
        plot.title = element_blank(),
        panel.grid = element_blank(),
        plot.title.position = "plot",
        plot.margin = margin(b = 5, r = 5, l = 5),
        panel.background = element_rect(color = "grey75", fill = NA, size = .4),
        strip.text = element_text(face = "bold"),
        strip.text.y = element_text(size = 12),
        strip.text.x = element_text(size = 12)) +
  scale_fill_manual(values = c("#502a7b","#502a7c","#502a7a" ))+
  guides(color = guide_legend(override.aes = list(size = .75)),
         fill =  guide_legend(override.aes = list(size = .75)),
         size = "none", linetype = guide_legend(override.aes = list(size = .75))) +
  coord_cartesian(ylim = c(0, 1), xlim = c(0,5))+
  scale_y_continuous(breaks = seq(0,1,0.25)) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5))

```



## Prediction Parameters 

### By Domain
```{r, warning=FALSE}

pred_df_domain <- NULL

for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= unique(df$domain),  
                 sei = 0.1,
                 item=NA, 
                 event=NA,
                 formulation=NA,
                 age_dec_c=0,
                 age_dec_c2=0,
                 female_c= 0, 
                 interval_val=0)
  
  
  
  
  fit_nlpar_domain <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA)    
  

 
  fit_nlpar_domain <- fit_nlpar_domain %>%
    group_by(domain) %>% 
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "domain",
           x = domain)%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  pred_df <- fit_nlpar_domain
  

  pred_df_domain <- bind_rows(pred_df, pred_df_domain) 
}



pred_df_domain <- pred_df_domain %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))

```



### By Item
```{r, warning=FALSE}

pred_df_item <- NULL

  
  
  for (curr_nlpar in c("stabch","rel","change")) {
    
    
    nd <- crossing(domain= NA,  
                   sei = 0.1,
                   item= unique(df$item), 
                   event=NA,
                   formulation=NA,
                   age_dec_c=0,
                   age_dec_c2=0,
                   female_c= 0, 
                   interval_val=0)
    
    
    fit_nlpar_item <- nd %>% 
      add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
    

  
    
    
    fit_nlpar_item <- fit_nlpar_item %>%
      group_by(item) %>% 
      mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
      pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
      mutate(nlpar = curr_nlpar,
             estimate = .epred,
             categ = "item",
             x = item)%>% 
      select(categ, x, nlpar, estimate, dplyr::contains("er_"))
    
    
    
    pred_df <- fit_nlpar_item
    
    
    pred_df_item <- bind_rows(pred_df, pred_df_item) 
  }
  

pred_df_item <- pred_df_item %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))

```


### By Event
```{r, warning=FALSE}

pred_df_event <- NULL



for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= NA,  
                 sei = 0.1,
                 item= NA, 
                 event=unique(df$event),
                 formulation=NA,
                 age_dec_c=0,
                 age_dec_c2=0,
                 female_c= 0, 
                 interval_val=0)
  
  
  fit_nlpar_event <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
  
  
  
  
  
  fit_nlpar_event <- fit_nlpar_event %>%
    group_by(event) %>% 
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "event",
           x = event)%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  
  pred_df <- fit_nlpar_event
  
  
  pred_df_event <- bind_rows(pred_df, pred_df_event) 
}

pred_df_event <- pred_df_event %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))


```


### By Formulation
```{r, warning=FALSE}

pred_df_formulation <- NULL



for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= NA,  
                 sei = 0.1,
                 item= NA, 
                 event=NA,
                 formulation= unique(df$formulation),
                 age_dec_c=0,
                 age_dec_c2=0,
                 female_c= 0, 
                 interval_val=0)
  
  
  fit_nlpar_formulation <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
  
  
  
  
  
  fit_nlpar_formulation <- fit_nlpar_formulation %>%
    group_by(formulation) %>% 
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "formulation",
           x = formulation)%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  
  pred_df <- fit_nlpar_formulation
  
  
  pred_df_formulation <- bind_rows(pred_df, pred_df_formulation) 
}

pred_df_formulation <- pred_df_formulation %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))
```


### By Age
```{r, warning=FALSE}

pred_df_age <- NULL



for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= NA,  
                 sei = 0.1,
                 item= NA, 
                 event=NA,
                 formulation=NA,
                 age_dec_c= c(-2,0,2,4),
                 age_dec_c2= c(4, 0, 4, 16),
                 female_c= 0, 
                 interval_val=0)
  
  
  fit_nlpar_age <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
  
  
  
  
  
  fit_nlpar_age <- fit_nlpar_age %>%
    group_by(age_dec_c) %>% 
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "age",
           x = case_when(age_dec_c== 4 ~ "80+", age_dec_c== 2 ~ "60-79", age_dec_c== 0 ~ "40-59", age_dec_c== -2 ~ "20-39"))%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  
  pred_df <- fit_nlpar_age
  
  
  pred_df_age <- bind_rows(pred_df, pred_df_age) 
}

pred_df_age <- pred_df_age %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))

```


### By Gender
```{r, warning=FALSE}

pred_df_female <- NULL



for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= NA,  
                 sei = 0.1,
                 item= NA, 
                 event=NA,
                 formulation=NA,
                 age_dec_c= 0,
                 age_dec_c2= 0,
                 female_c= c(-0.5, 0.5), 
                 interval_val=0)
  
  
  fit_nlpar_female <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
  
  
  
  
  
  fit_nlpar_female <- fit_nlpar_female %>%
    group_by(female_c) %>% 
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "gender",
           x = ifelse(female_c== -0.5, "male", "female"))%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  
  pred_df <- fit_nlpar_female
  
  
  pred_df_female <- bind_rows(pred_df, pred_df_female) 
}

pred_df_female <- pred_df_female %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))

```


### Overall
```{r, warning=FALSE}

pred_df_overall <- NULL



for (curr_nlpar in c("stabch","rel","change")) {
  
  
  nd <- crossing(domain= NA,  
                 sei = 0.1,
                 item= NA, 
                 event=NA,
                 formulation=NA,
                 age_dec_c= 0,
                 age_dec_c2= 0,
                 female_c= 0, 
                 interval_val=0)
  
  
  fit_nlpar_overall <- nd %>% 
    add_epred_draws(fit_masc_m3, nlpar = curr_nlpar, re_formula = NA) 
  
  
  
  
  
  fit_nlpar_overall <- fit_nlpar_overall %>%
    mean_hdci(.epred,.width = c(.95,.8,.5)) %>% 
    pivot_wider(names_from = .width, values_from = c(.lower,.upper)) %>% 
    mutate(nlpar = curr_nlpar,
           estimate = .epred,
           categ = "all",
           x = "overall")%>% 
    select(categ, x, nlpar, estimate, dplyr::contains("er_"))
  
  
  
  pred_df <- fit_nlpar_overall
  
  
  pred_df_overall <- bind_rows(pred_df, pred_df_overall) 
}


pred_df_overall <- pred_df_overall %>% 
  mutate(nlpar = case_when(nlpar == "rel" ~ "Reliability",
                           nlpar == "change" ~ "Change",
                           nlpar == "stabch" ~"Stab. Change"))


pred_df <- bind_rows(pred_df_domain, pred_df_item, pred_df_event, pred_df_formulation ,pred_df_age, pred_df_female, pred_df_overall)


```



## Parameters Table
```{r, warning=FALSE}
library(gt)

# Selecting only the specified columns from pred_df
pred_df_selected <- pred_df[, c("categ", "x", "nlpar", "estimate", ".lower_0.95", ".upper_0.95")]

# Create a gt table
table_gt <- gt(data = pred_df_selected,
               rowname_col = "x",
               caption = "Prediction Results",
               rownames_to_stub = TRUE)

# Formatting
table_gt <- table_gt %>%
  tab_header(title = "Estimates and Confidence Intervals") %>%
  fmt_number(columns = c("estimate", ".lower_0.95", ".upper_0.95"), decimals = 3) %>%
  cols_align(align = "center") 

table_gt

```


## Parameters Plot
```{r, warning=FALSE}

pred_df <- pred_df %>%
  mutate(categ = str_to_title(as.character(categ)),
         x = str_to_title(as.character(x)))


pred_df$nlpar <- factor(pred_df$nlpar, levels = c("Reliability", "Change", "Stab. Change"))


pred_df$x <- factor(pred_df$x, levels = c("Overall", "None","Event", "Other", "Health",  "Single", "Multiple", "Threat", "Concern", "Worry", "Risk", "80+","60-79", "40-59", "20-39", "Male", "Female"))

pred_df$categ <- factor(pred_df$categ, levels = c("All", "Event", "Domain",  "Item", "Formulation"  ,"Age", "Gender"))


p_nlpar <- pred_df %>% ggplot() +
  geom_crossbar(aes(xmin = .lower_0.95, x = estimate, 
                    xmax = .upper_0.95, y = x),
                fill = "white", color = "NA",
                linewidth = .15,width = 0.25, alpha =  1) +
  geom_crossbar(aes(xmin = .lower_0.95, x = estimate, 
                    xmax = .upper_0.95, y = x),
                fill = "#502a7a", color = "NA",
                linewidth = .15,width = 0.25, alpha =  .3) +
  geom_crossbar(aes(xmin = .lower_0.8, x = estimate,
                    xmax = .upper_0.8, y = x),
                fill = "white", color = "NA",
                linewidth = .15,width = 0.25, alpha =  1) +
  geom_crossbar(aes(xmin = .lower_0.8, x = estimate,
                    xmax = .upper_0.8, y = x),
                fill = "#502a7a",color = "NA",
                linewidth = .15,width = 0.25, alpha =  .6) +
  geom_crossbar(aes(xmin = .lower_0.5, x = estimate, 
                    xmax = .upper_0.5, y = x),
                fill = "white",color = "NA",
                linewidth = .15,width = 0.25, alpha =  1) +
  geom_crossbar(aes(xmin = .lower_0.5, x = estimate, 
                    xmax = .upper_0.5, y = x),
                fill = "#502a7a",color = "NA",
                linewidth = .15,width = 0.25, alpha =  .9) +
  geom_point(aes(x = estimate, y =x),
             fill = "white", color = "grey20",
             shape = 21, 
             stroke = .25, 
             size = 2) +
  facet_grid(categ ~ nlpar, scales = "free_y", space = "free", switch = "y") + 
  # scale_x_continuous(limits = c(0,1), expand = c(0,0)) +
  scale_x_continuous(limits = c(0, 1), expand = c(0, 0), breaks = c(0, 0.5, 1), labels = c("0", "0.5", "1")) +
  scale_y_discrete(position = "left") +
  theme_minimal() +
  geom_rect(data = subset(pred_df, x %in% c("Overall")), 
            fill = NA, colour = "black", size = .75, xmin = -Inf,xmax = Inf,
            ymin = -Inf,ymax = Inf) +
  theme(panel.grid = element_blank(),
        legend.position = "none",
        plot.title.position = "plot",
        strip.placement = "outside",
        #strip.text.y = element_blank(),
        axis.title.x = element_text(size = 10, color = "grey20"),
        plot.margin = margin(b = 10, t = 10, r = 15, l = 0),
        panel.spacing.x = unit(.3, "cm"),
        # plot.tag.position = c(0.025,.9),
        # panel.grid.major.x = element_line(linewidth = .2, color = "grey80", linetype = "solid"),
        panel.background = element_rect(linewidth = .25, color = "grey50", fill = "NA"),
        #plot.background = element_rect(linewidth = .25, color = "grey40", fill = "NA"),
        strip.text =  element_text( face = "bold"),
        strip.text.y = element_text(size = 10),
        strip.text.x = element_text(size = 10),
        plot.tag  = element_text( size = 10, face = "bold", color = "grey20"),
        plot.title = element_blank(),
        title = element_text( face = "bold", size = 10),
        axis.text.x =  element_markdown( color = "black", size = 10, hjust=c(0,.5, 1)),
        axis.text.y.left =  element_markdown( angle = 0, hjust = 1, color = "grey20", size = 10), # hjust = c(0,.5,.5,.5,1)
        text = element_text()) +
  labs(y = "", x = "Parameter Estimate", title = "Propensity") 


p_nlpar

ggsave(plot = p_nlpar,
       filename = here::here("analysis", "masc_pred.jpeg"), 
       dpi = 300, width = 28, height = 30, units = "cm") 

```

